Characterization and evolution of hourly extreme precipitation in France using an Explicit-Convection Regional Climate Model

### 2025-11-10 article/fig8.qmd
figs independant

combined = combined_metrics_df("metrics.csv")

@@

selected_seasons = ["hydro", "djf", "mam", "jja", "ond", "jfm", "amj", "jas", "avr", "mai", "jui"]
to_plot = combined[combined["season"].isin(selected_seasons)]
plot_r_by_season(to_plot, echelles=['quotidien', 'quotidien_reduce', 'horaire'], col_values=['numday', 'mean', 'mean-max'], nom_fichier="histo_numday_mean_mean-max")
```

```{=latex}
\par\noindent
\makebox[\linewidth][c]{%
\includegraphics[width=\linewidth,keepaspectratio]{\detokenize{figures/histo_numday_mean_mean-max.pdf}}%
}
\par
```

>>>>

combined = combined_metrics_df("metrics.csv")
combined_signif = combined_metrics_df("metrics_signif.csv")
combined_signif["col_calculate"] = combined_signif["col_calculate"].astype(str) + "_signif"
combined_all = pd.concat([combined, combined_signif], ignore_index=True)

@@

selected_seasons = ["hydro", "ond", "jfm", "amj", "jas", "jan", "fev", "mar", "avr", "mai", "jui", "juil", "aou", "sep", "oct", "nov", "dec"]
to_plot = combined_all[combined_all["season"].isin(selected_seasons)]
plot_r_by_season(to_plot , echelles=['quotidien', 'quotidien_reduce', 'horaire'], col_values=['z_T_p', 'z_T_p_signif'], nom_fichier="histo_z_T_p")
```

```{=latex}
\par\noindent
\makebox[\linewidth][c]{%
\includegraphics[width=\linewidth,keepaspectratio]{\detokenize{figures/histo_z_T_p.pdf}}%
}
\par
```
